Estimating Learning Dynamics in the Routing Game

### 2015-10-14 paper/paper.tex
Update.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\begin{figure*}
  \centering
  \includegraphics[width=160mm]{images/user_interface}
  \caption{Web interface for the routing game.}
  \label{fig:web_interface}
\end{figure*}
%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Game interface}

We simulate the proposed methods with a routing game interface that implements the behavior of the network. Players are assigned a unique origin and destination node pair and are tasked to assign a flow distribution to the paths between this pair at each turn of the game. The game calculates the cost along each edge of the network after all players have submitted their flow distribution for the turn. Each player then receives feedback with the local information of the cost for each path. The players then use this path cost history to assign a new flow distribution at the subsequent turns with the objective of minimizing their cumulative path cost.

@@

We can estimate the learning rate of each player with the update in \ref{eq:estimation_eta}. We can see that the learning rates of some players are negative at certain turns, which may be explained by the players assuming a contrarian play style at flow distribution assignments for those certain turns.

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/learning_rate}
  \caption{Learning rate for each player.}
  \label{fig:learning_rates}
\end{figure}

@@

\begin{figure}
  \centering
  % \includegraphics[width=80mm]{images/fill_me}
  \missingfigure[figwidth=6cm]{Testing a long text string}
  \caption{Flow distribution predictions moving average $\eta_t$.}
  \label{fig:moving_eta_predictions}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=80mm]{images/fill_me}
  \missingfigure[figwidth=6cm]{Testing a long text string}
  \caption{Flow distribution predictions linear regression $\eta_t$.}
  \label{fig:linear_regression_eta_predictions}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=80mm]{images/fill_me}
  \missingfigure[figwidth=6cm]{Testing a long text string}
  \caption{Flow distribution predictions parameterized $\eta_t$.}
  \label{fig:parameterized_eta_predictions}
\end{figure}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=80mm]{images/no_slider_global_potential_function}
%   \caption{Global potential function.}
%   \label{fig:global_potential_function}
% \end{figure}

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\begin{figure*}
  \centering
  \includegraphics[width=160mm]{images/user_interface}
  \caption{Web interface for the routing game.}
  \label{fig:web_interface}
\end{figure*}
%-----------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Setup}

We simulate the proposed methods with a routing game system that implements the behavior of the network. Players are assigned a unique origin and destination node pair and are tasked to assign a flow distribution to the paths between this pair at each turn of the game. The game calculates the cost along each edge of the network after all players have submitted their flow distribution for the turn. Each player then receives feedback with the local information of the cost for each path. The players then use this path cost history to assign a new flow distribution at the subsequent turns with the objective of minimizing their cumulative path cost.

@@

We can estimate the learning rate of each player with the update in Figure~\ref{eq:estimation_eta}. We can see that the learning rates of some players are negative at certain turns, which may be explained by the players assuming a contrarian play style at flow distribution assignments for those certain turns.

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/learning_rates}
  \caption{Learning rate for each player.}
  \label{fig:learning_rates}
\end{figure}

@@

% \begin{figure}
%   \centering
%   % \includegraphics[width=80mm]{images/fill_me}
%   \missingfigure[figwidth=6cm]{Testing a long text string}
%   \caption{Flow distribution predictions moving average $\eta_t$.}
%   \label{fig:moving_eta_predictions}
% \end{figure}

% \begin{figure}
%   \centering
%   % \includegraphics[width=80mm]{images/fill_me}
%   \missingfigure[figwidth=6cm]{Testing a long text string}
%   \caption{Flow distribution predictions linear regression $\eta_t$.}
%   \label{fig:linear_regression_eta_predictions}
% \end{figure}

% \begin{figure}
%   \centering
%   % \includegraphics[width=80mm]{images/fill_me}
%   \missingfigure[figwidth=6cm]{Testing a long text string}
%   \caption{Flow distribution predictions parameterized $\eta_t$.}
%   \label{fig:parameterized_eta_predictions}
% \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/two_steps_ahead_prediction}
  \caption{Two step prediction ahead for parameterized learning rate.}
  \label{fig:parameterized}
\end{figure}
